A graph-based data model for interactive evolutionary computation

### 2017-01-20 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
correcting duplicate labels
Abstract updated

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Interactive evolution is the leading technique employed by 
Evolutionary Art researchers, where users' preferences guide the search. A common
practice is to develop Interactive Evolutionary Computation (IEC) algorithms
as web applications in order to give users easy access the application as they
often depend on volunteers who visit the system to interactively help with the search. 
There are several drawbacks that limit user participation 
such as human fatigue and boredom resulting from evaluating 
a large number of individuals. 
To tackle this issues, we propose the design of IEC systems using a user-centered 
approach, with a framework consisting of a social network of 
volunteers, interacting with a population consisting again of a network 
of individuals. In this work we propose a graph model as a viable 
and efficient tool for mapping in a natural way the relationships 
found in the system. A case study is presented as a proof of concept, 
providing both conceptual and implementation details of a graph based model 
as it is 
applied in the implementation of an IEA using the EvoSpace-Interactive platform. 
As a result, the graph model was then succesfully applied to measure the degree
of relationship between users with the porpuse of quantifing 
their participation.

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=3.5in]{img/framework.png}
    \caption{IEC Human-centered framework.}
    \label{fig:web}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{Sample of users, showing the {\tt knows} relationship.}
    \label{fig:top-users}
\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Interactive evolution is the leading technique employed by 
Evolutionary Art researchers, where users' preferences guide the search. A common
practice is to develop Interactive Evolutionary Computation (IEC) algorithms
as web applications in order to give users easy access the application as they
often depend on volunteers who visit the system to interactively help with the search. 
There are several drawbacks that limit user participation 
such as human fatigue and boredom resulting from evaluating 
a large number of individuals. 
To tackle this issues, we propose the design of IEC systems using a human-centered 
approach, with a framework consisting of a social network of 
volunteers, interacting with a population consisting also of a network 
of individuals. In this work we propose a graph model as a practical 
and efficient tool for mapping in a natural way the relationships 
found in the system. A case study is presented as a proof of concept, 
providing both conceptual and implementation details of a graph based model 
as it is  applied in the implementation of an IEA using the EvoSpace-Interactive platform. 
As a result, the graph model was successfully applied in a gamification technique 
developed to increase user engagement.

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=3.5in]{img/framework.png}
    \caption{IEC Human-centered framework.}
    \label{fig:uc_framework}
\end{figure*}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{Sample of users, showing the {\tt knows} relationship.}
    \label{fig:users-graph}
\end{figure}
